---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mardyr2

<!-- badges: start -->
<!-- badges: end -->

mardyr2 enables the user to select, visualize and download
data from the MARDY-research project. Additional functionalities include access to
training models via an API, the `DEbateNet-mig15`-data set, and utility functions.

This software is part of the following publication:

>  Lapesa, G., Blessing, A., Blokker, N., Dayanik, E., Haunss, S., Kuhn, J., Pado, S.: 
 DEbateNet-mig15: Tracing the 2015 Immigration Debate in Germany Over Time. 
 In: Proceedings of LREC. , Marseille, France (2020). 

## License

See [here](https://clarin09.ims.uni-stuttgart.de/debatenet/) for further information regarding the licensing. 


## Installation

You can find the LREC release version of mardyr2 [here](https://clarin09.ims.uni-stuttgart.de/debatenet/). 
To install the development version please run: 

``` r
devtools::install_gitlab(https://github.com/nicoblokker/mardyr_dev)
```

## Examples

Load and access the DEbateNet-15mig data set:

```{r example0, eval=T, message=F}
library(mardyr2)
data("DEbateNet_mig15")
dim(DEbateNet_mig15)
```

Start `shinyApp` to visualize the `DEbateNet-mig15` data set

```{r example, eval=F}
library(mardyr2)
get_data(source = "example")
```

Or send a test sentence to the API:

```{r example2, eval=T, message=F}
library(mardyr2)
get_predictions("Angela Merkel lehnt eine Obergrenze ab.", output = "word")
```

Access the documentation for further examples (`help(package = "mardyr2")`).
